Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-05-30 outputs/paper/paper.qmd
Installed sf package for upcoming mapping of subdivision data.
Also, using example code referenced from 2 places, I put together a table using cleaned voting locations data, which shows subdivision, ward/subdivision numbers combined, and subdivision addresses.

## Load packages
library(tidyverse)
library(knitr)
library(here)

@@

### Election Voting Locations
This dataset, published by the City Clerk's Office [@VotingLocations] highlights all polling locations and subdivisions, on a ward-by-ward basis from the 2022 municipal election. This data was last refreshed on November 2, 2022 and captured for this paper on May 21, 2023. The polling locations account for Advance Vote, election day, and Mail In Voting. One subdivision in a ward is equivalent to one polling location, based on geography. In each ward, subdivision 97 accounts for Mail In Voting, while subdivisions 98 and 99 are designated Advance Vote locations. Voters can request a Mail In ballot, go to one of the two Advance Vote locations during the designated days, or vote at their assigned subdivision on election day (for example: ward 11, subdivision 11).

@@

# code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
head (cleaned_voter_statistics, 5) |>
  kable(
    col.names = c("Ward", "Sub", "Total Eligible Electors",	"Number Voted",	"Percent Voted"),
  booktabs = TRUE
  )

>>>>

## Load packages
library(tidyverse)
library(knitr)
library(here)
library(sf)

@@

### Election Voting Locations
This dataset, published by the City Clerk's Office [@VotingLocations] highlights all polling locations and subdivisions, on a ward-by-ward basis from the 2022 municipal election. This data was last refreshed on November 2, 2022 and captured for this paper on May 21, 2023. The polling locations account for Advance Vote, election day, and Mail In Voting. One subdivision in a ward is equivalent to one polling location, based on geography. In each ward, subdivision 97 accounts for Mail In Voting, while subdivisions 98 and 99 are designated Advance Vote locations. Voters can request a Mail In ballot, go to one of the two Advance Vote locations during the designated days, or vote at their assigned subdivision on election day (for example: Ward 11, Subdivision 11).

```{r}
#| message: false
#| echo: false
#| label: tbl-cleaned_voting_location
#| tbl-cap: Sample of Cleaned Voting Locations Data

# code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
# & https://tellingstorieswithdata.com/20-r_essentials.html 
head (cleaned_voting_locations, 5) |>
  select(point_short_code, point_long_code, address_full) |>
  kable(
    col.names = c("Subdivision", "Ward & Subdivision", "Address"),
  booktabs = TRUE
  )

@@

head (cleaned_voter_statistics, 5) |>
  kable(
    col.names = c("Ward", "Sub", "Total Eligible Electors",	"Number Voted",	"Percent Voted"),
  booktabs = TRUE
  )
